Irreducible Components and Dimension of the Springer Fiber of a Hook-Type Slodowy Slice

### 2024-09-02 paper.tex
fix proof of 5.2

\begin{lemma}\label{pwr_union}
    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
\end{lemma}
\begin{proof}
    For any \(a \in \mathbb{C}^m\), define the linear map \(\phi_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_j \mapsto 0\).
    Note that \(A_{a,b}\) is the unique linear map \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + \phi_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
    \par Let \((A_{a, b}, V_\bullet) \in \mathcal{P}\).
    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n)\) for some \(a',b' \in \mathbb{C}^m\).
    All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
    Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
\end{proof}
\begin{lemma}
    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
\end{lemma}
\begin{proof}
    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
    \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
    Let \(k \geq 0\) be minimal so that \(A_{e_{w_1r_1},0} f_1 \neq 0\).
    Obviously \(k = r_1\).
    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2\).
    Hence \(r_1 = r_2\).
    Now, if \(r_1 = 0\), we are done.
    \par Otherwise, \(r_1 > 0\).
    Let \(k' \geq 0\) be maximal such that \(\exists v \in \mathbb{C}^m. \; A_{e_{w_1r_1},0}^{k'} v = A_{e_{w_1r_1},0} f_1\).
    Obviously \(k' = \lambda_{w_1} - r_1\).
    Clearly \(k'\) is independent of \(\mathbb{C}^m\)-basis, so \(\lambda_{w_1} - r_1 = k' = \lambda_{w_2} - r_2\).
\end{proof}

>>>>

\begin{lemma}\label{pwr_union}
    \(\mathcal{P} = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} \mathcal{P}_{wr}\).
\end{lemma}
\begin{proof}
    For any \(a \in \mathbb{C}^m\), define the linear map \(\phi_a : \mathbb{C}^{m + n} \to \mathbb{C}\) by \(e_{ij} \mapsto a_{ij}\) and \(f_j \mapsto 0\).
    Note that \(A_{a,b}\) is the unique linear map \(\mathbb{C}^{m + n} \to \mathbb{C}^{m + n}\) that sends \(e_{ij}\) to \(e_{i,j-1} + \phi_a(e_{ij}) f_n\), sends \(f_{i + 1}\) to \(f_i\), and sends \(f_1\) to \((b, 0)\).
    \par Let \((A_{a, b}, V_\bullet) \in \mathcal{P}\).
    Since \(X\) is nilpotent, \cref{normalization} says that there is a change of basis \(P : \mathbb{C}^m \to \mathbb{C}^m\) such that the vectors \(Pe_{ij}\) form a Jordan basis for \(X\), and for all but one pair \((i, j)\) we have \(\phi_a(Pe_{ij}) = 0\).
    \par Since \((Pe_{ij})_{ij}\) is a Jordan basis, we have \((P^{-1}, I_n) A_{a,b}(P, I_n)\) for some \(a',b' \in \mathbb{C}^m\).
    All that is left is to show that \(a'\) is of the form \(e_{wr}\) for some \(w\) and \(r\).
    Indeed, this results from the fact that \(\phi_{a'}(e_{ij}) = \phi_a(Pe_{ij}) = 0\) for all but one pair \((i,j)\).
\end{proof}
\begin{lemma}
    \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\).
\end{lemma}
\begin{proof}
    If \(r_1 = r_2 = 0\), we have \(e_{wr_1} = e_{wr_2} = 0\), so by definition, \(\mathcal{P}_{wr_1} = \mathcal{P}_{wr_2}\).
    And if \((\lambda_{w_1}, r_1) = (\lambda_{w_2}, r_2)\), then any matrix of the form \(A_{e_{w_1r_1}b'}\) can be transformed to a matrix of the form \(A_{e_{w_2r_2}b'}\) by making the change of basis that swaps \(e_{w_1j}\) with \(e_{w_2j}\).
    \par Conversely, suppose \(\mathcal{P}_{w_1r_1} = \mathcal{P}_{w_2r_2}\).
    Clearly either \(r_1 = r_2 = 0\) or \(r_1 \neq 0\) and \(r_2 \neq 0\).
    In the first case, we're done.
    \par Otherwise, let \(k \geq 0\) be minimal such that there exist \(u,v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0} (u,0) = (v,0) + f_n\) and \(A_{e_{w_1r_2},0}^k (v,0) = 0\).
    Obviously \(k = r_1 - 1\).
    Since (by hypothesis) \(A_{e_{w_1r_1},0}\) and \(A_{e_{w_2r_2},0}\) differ only by a change of basis of \(\mathbb{C}^m\), the same reasoning shows that \(k = r_2 - 1\).
    Hence \(r_1 = r_2\).
    Now we only need to show that \(\lambda_{w_1} = \lambda_{w_2}\).
    \par Let \(k' \geq 0\) be maximal such that there exist \(u,v \in \mathbb{C}^m\) with \(A_{e_{w_1r_1},0}^{k'} (u,0) = (v,0) + f_n\).
    Obviously \(k' = \lambda_{w_1} - r_1 + 1\).
    Since \(k'\) is independent of \(\mathbb{C}^m\)-basis, we get \(\lambda_{w_1} - r_1 + 1 = k' = \lambda_{w_2} - r_2 + 1\), and therefore \(\lambda_{w_1} = \lambda_{w_2}\).
\end{proof}
